---
title: "FML_project"
author: "Momo"
date: "22/02/2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Federal

Information on the 42nd Parliament members were retrieved from [here](https://www.ourcommons.ca/members/en/search?parliament=42&caucusId=all&province=all&gender=all&view=list).
Emily has already populated data for the (current) members of the 43rd Parliament.

I am going to read in the csv files for raw 42nd and 43rd member csv files. 

```{r 42nd}
fourtysecond<-read.csv("42nd.csv", header=TRUE, sep=",", encoding="UTF-8")
fourtythird<-read.csv("43rd.csv", header=TRUE, sep=",", encoding="UTF-8")
```

Loading in necessary libraries here:
```{r warning=FALSE, message=FALSE}
library(dplyr)
library(tidyverse)
 
```
I will extract data already gathered for 43rd MPs (by Emily) and add it to 42nd MP data

```{r message=F}
bind<-left_join(fourtysecond, fourtythird)
fourtysecond_data<-bind%>%
  select(1:13, 17:18)


```


Find out how many 42nd MPs have no data. 

```{r }
missing<-anti_join(fourtysecond, fourtythird)
```
**We need to gather data for `r nrow(anti_join(fourtysecond, fourtythird))` MPs.** 
And saving the file with the names of MPs that are missing info.

```{r eval=F}
write.csv(missing, "42nd_missing_info.csv")
```



## Web scraping wiki
Loading the libraries that are needed
```{r warning=FALSE, message=FALSE }
library(XML)
library(rvest)
library(dplyr)
```

Here are the names of the MPs with missing birth dates
```{r}
Name <-missing%>%
  select(First.Name, Last.Name)%>%
  unite(Full, First.Name, Last.Name, sep=" ", remove=FALSE)
Name

```
And here is the function and loop for grabbing birth years from wikipedia

```{r}
person<-"Rona Ambrose"
  
 FUN<- function(person) {
    link <- paste0("https://en.wikipedia.org/wiki/", str_replace_all(person, " ", "_"))
    
    wiki <- read_html(link)
    
    
    tab<-wiki%>%
      html_nodes("table")%>%
      html_table(fill=TRUE)%>%
      .[[1]]
    bd<-tab%>%
      rename(col1=1)%>%
      rename(col2=2)%>%
      filter(col1=="Born")
    bd%>%
      select(col2)
  }

Name$Birth.Date <- ""
for (i in 1:nrow(Name)) {
  tryCatch({
    Name$Birth.Date[i] <- FUN(Name$Full[i])
    print(paste("Got bday for", Name$Full[i]))
  }, error = function(e) {
    print(paste("Error for", Name$Full[i]))
  })
}

Name
```

Subsetting to prepare for joining with original "42nd_data.csv" file

```{r}
subName<-Name%>%
  select(Last.Name, Birth.Date)
  
```



Now I will bring the data into to the "42nd_data.csv" file.

```{r}
df<-left_join(fourtysecond_data, subName, by=
                 "Last.Name")
fourtysecond_new<-apply(df, 2, as.character)
```

Save new 42nd MP data file.
```{r eval=F}
write.csv(fourtysecond_new, "42nd_data.csv")

```
I definitely need some help cleaning it a little bit by deleting all the unnecessary information that came along with the birth dates!



