---
title: "Momo's code"
author: "Momo"
date: "24/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Updating the csv

Some wiki sites had "(politician)" next to their names so I will try to scrape those names. I will first extract the rows with missing birthdays. 


Load libraries
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(stringr)
library(tidyr)
```

Read csv file
```{r}
allmps<-read.csv("all_MPs_bd_3.csv", header=TRUE, sep=",", encoding="UTF-8", na.strings = c("","NA"))
head(allmps)

```
Extract rows with missing Birth.Dates

```{r}
missing<-allmps%>%
  select(Full, Birth.Date_raw)%>%
  filter_all(any_vars(is.na(.)))%>%
  mutate(politician="(politician)")%>%
  mutate(Full_new= Full)%>%
  unite(Full_new, Full_new,politician)
head(missing)
```
Loading libraries needed
```{r warning=FALSE, message=FALSE }
library(XML)
library(rvest)
```
And here is the function for grabbing birth years for those names with "(politician)" next to their name -  from wikipedia table

```{r}
person<-"Peter Adams_(politician)"
  
 BD<- function(person) {
    link <- paste0("https://en.wikipedia.org/wiki/", str_replace_all(person, " ", "_"))
    link
    wiki <- read_html(link)
    
    
    tab<-wiki%>%
      html_nodes("table")%>%
      html_table(fill=TRUE)%>%
      .[[1]]
    bd<-tab%>%
      rename(col1=1)%>%
      rename(col2=2)%>%
      filter(col1=="Born")
    bd%>%
      select(col2)
  }

```  

And here is the function for grabbing occupation from wiki table
```{r}
 OC<- function(person) {
    link1 <- paste0("https://en.wikipedia.org/wiki/", str_replace_all(person, " ", "_"))
    wiki1 <- read_html(link1)
    
    
    tab1<-wiki1%>%
      html_nodes("table")%>%
      html_table(fill=TRUE)%>%
      .[[1]]
    oc<-tab1%>%
      rename(col1=1)%>%
      rename(col2=2)%>%
     slice(3:3)
    oc%>%
      select(col2)
  }
```
Here is the loop to grab birth date and occupation

```{r}
missing$Birth.Date <- ""
for (i in 1:nrow(missing)) {
  tryCatch({
    missing$Birth.Date[i] <- BD(missing$Full_new[i])
    print(paste("Got bday for", missing$Full_new[i]))
  }
  , error = function(e) {
    print(paste("Error for", missing$Full_new[i]))
  }
)
}
```

Now I will bring the data into to the original "all_MPs" file.

```{r}
tent<-missing%>%
  mutate(Birth.Date_raw=Birth.Date)
tent1<-tent%>% 
mutate(Birth.Date_raw=sapply(Birth.Date_raw, toString))%>%
  select(Full, Birth.Date_raw)
head(tent1)

df1<-left_join(allmps, tent1, by="Full")
head(df1)
df2<-df1%>%
  coalesce(Birth.Date_raw.x, Birth.Date_raw.y)

allmps<-df%>%
  mutate(Birth.Date=sapply(Birth.Date, toString))%>%
  mutate(Occupation=sapply(Occupation, toString))


head(allmps)  
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
