---
title: "Part 2: Double check data on birth dates"
author: "Momo"
date: "12/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Parse birth date

First, read the .csv file with initial collection of birth dates from part 1. 
```{r}

bd_part1<-read.csv("all_MPs_bd.csv", header=TRUE, sep=",", encoding="UTF-8-BOM")
head(bd_part1)
```

Load libraries
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(stringr)
library(tidyr)
```

Change "Birth.Date" column to "Birth.Date_raw"

```{r}
bd_part2<-bd_part1%>%
  mutate(Birth.Date_raw=Birth.Date)%>%
  select(-Birth.Date)
head(bd_part2)
```


Parse date from Birth.Date_raw column

```{r}
bd_part1_parse<-bd_part2%>%
  dplyr::mutate(Birth.Date=str_extract(Birth.Date_raw, "(?<=[(])[^)]+"))
head(bd_part1_parse)
```
Add "Start_date" and "End_date" columns for the time in office

```{r}
start<-bd_part1_parse%>%
  dplyr::mutate(Start_date=str_extract(Political.Affiliation, "(?<=[(])[^-]+"))%>%
  dplyr::mutate(End_date=str_extract(Political.Affiliation, "(?<=[-])[^)]+"))
head(start)
```

Save part2 42nd MP data file.
```{r eval=F}
write.csv(start, "all_MPs_bd_2.csv")

```

## Checking against Emily's 43rd data
Load libraries
```{r message=FALSE, warning=FALSE}
library(tidyr)
```

Load 43rd data
```{r}
MPs_2<-read.csv("all_MPs_bd_2.csv", header=TRUE, sep=",", encoding="UTF-8-BOM" )
fourtythird<-read.csv("43rd.csv", header=TRUE, sep=",", encoding="UTF-8")
head(fourtythird)
head(MPs_2)
```

Add column "Full" in fourtythird dataframe.

```{r}
Full<-fourtythird%>%
  unite(Full, First.Name, Last.Name, sep=" ", remove=FALSE)%>%
  select(Full, Birth.Date)
head(Full)
```

Bring in birthdates for 43rd members into all_MPs spreadsheet

```{r}
bind<-left_join(MPs_2, Full, by="Full")
head(bind)
```

Update the "Birth.Date" column by filling in missing birth dates from 43rd MP list

```{r}
colnames(bind)
all_MPs_3<-bind%>%
  mutate(Birth.Date.x=coalesce(Birth.Date.x, Birth.Date.y))%>%
  mutate(Birth.Date=Birth.Date.x)
all_MPs_3a<-all_MPs_3%>%select(-Birth.Date.x, -Birth.Date.y)
colnames(all_MPs_3a)
```

Save new 42nd MP data file.
```{r eval=F}
write.csv(all_MPs_3a, "all_MPs_bd_3.csv")
```



