---
title: "MPs (1968 to current)"
author: "Momo"
date: "12/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Federal

Information on the Parliament members from 1968 to current.  

I will read in the csv file.  

```{r 42nd}
allmps<-read.csv("all_MPs.csv", header=TRUE, sep=",", encoding="UTF-8")
head(allmps)
```

Loading in necessary libraries here for data wrangling:
```{r warning=FALSE, message=FALSE}
library(dplyr)
library(tidyverse)
```


## Web scraping from wiki
Loading the libraries that are needed
```{r warning=FALSE, message=FALSE }
library(XML)
library(rvest)
```

I will need to create a new column with the names appearing as First-Middle-Last rather than Last, First.
```{r}
allmps<-allmps%>%
  rename(Name=1)

allmps$Name2<-sub("(\\w+),\\s(\\w+)","\\2 \\1", allmps$Name)

get.first.name <- function(Name2) {
  lapply(ifelse(grepl(",",Name2),strsplit(Name2,","),strsplit(Name2," ")),`[[`,1)
}

get.last.name <- function(Name2) {
  d <- lapply(ifelse(grepl(",",Name2),strsplit(Name2,","),strsplit(Name2," ")),`[[`,2)
  lapply(strsplit(gsub("^ ","",d), " "),`[[`,1)
}

allmps_new <- allmps %>% 
  mutate(first.name=get.first.name(Name2),
                     last.name=get.last.name(Name2))%>%
  unite(Full, first.name, last.name, sep=" ", remove=FALSE)
```


I now have a column "Full" that can be used to scrape on wiki
```{r}
head(allmps_new)
```
Creating a subset with just Full name
```{r}
Name<-allmps_new%>%
  select(Full)

```


And here is the function for grabbing birth years from wikipedia table

```{r eval=F}
person<-"Rona Ambrose"
  
 BD<- function(person) {
    link <- paste0("https://en.wikipedia.org/wiki/", str_replace_all(person, " ", "_"))
    
    wiki <- read_html(link)
    
    
    tab<-wiki%>%
      html_nodes("table")%>%
      html_table(fill=TRUE)%>%
      .[[1]]
    bd<-tab%>%
      rename(col1=1)%>%
      rename(col2=2)%>%
      filter(col1=="Born")
    bd%>%
      select(col2)
  }

```  

And here is the function for grabbing occupation from wiki table
```{r}
 OC<- function(person) {
    link1 <- paste0("https://en.wikipedia.org/wiki/", str_replace_all(person, " ", "_"))
    
    wiki1 <- read_html(link1)
    
    
    tab1<-wiki1%>%
      html_nodes("table")%>%
      html_table(fill=TRUE)%>%
      .[[1]]
    oc<-tab1%>%
      rename(col1=1)%>%
      rename(col2=2)%>%
     slice(3:3)
    oc%>%
      select(col2)
  }
```
Here is the loop to grab birth date and occupation

```{r eval=FALSE}
Name$Birth.Date <- ""
for (i in 1:nrow(Name)) {
  tryCatch({
    Name$Birth.Date[i] <- BD(Name$Full[i])
    print(paste("Got bday for", Name$Full[i]))
  }
  , error = function(e) {
    #print(paste("Error for", Name$Full[i]))
  }
)
}

Name$Occupation <- ""
for (i in 1:nrow(Name)) {
  tryCatch({
    Name$Occupation[i] <- OC(Name$Full[i])
    print(paste("Got occupation for", Name$Full[i]))
  }
  , error = function(e) {
    #print(paste("Error for", Name$Full[i]))
  }
)
}
```



Now I will bring the data into to the original "all_MPs" file.

```{r}
head(allmps_new)
allmps_new<-allmps_new%>%
  select(-first.name, -last.name, -Name2)
df<-left_join(allmps_new, Name, by=
                 "Full")
head(df)

allmps<-df%>%
  mutate(Birth.Date=sapply(Birth.Date, toString))%>%
  mutate(Occupation=sapply(Occupation, toString))


head(allmps)  
```

Save new 42nd MP data file.
```{r eval=F}
write.csv(allmps, "all_MPs_bd.csv")

```


